### 2017-07-19 architecture.tex
Whitespace cleanup
Fixing export control
Clarifying treatment of results

\textbf{ExportControl:} Specifies if derived or copied data
can be exported outside of the safe collection.

@@

Stewards are responsible for activities such as approving access to a collection, reviewing
export requests, and managing policies on the collection. 
As described above, stewards are pre-associated with a particular safe collection by
way of a specialized role and mapping to a collection's storage layer. 
External users (e.g., analysts) can discover
and then obtain access to safe collections by listing available safe collections and requesting
access to individual collections.
Stewards for a safe collection are presented with a list of user requests and must explicitly approve access
for a specific duration. Throughout the duration of a user's access to a collection
stewards may review their actions and revoke access at any time. When users attempt
to export data from an export controlled safe-collection, the data is not immediately
accessible to the user. Rather, the exported data is collected and stored privately
such that a steward can approve the export request.

>>>>

\textbf{ExportControl:} Specifies policy on export of derived or copied data
from safe collection such as steward review process.

@@

Stewards are responsible for activities such as approving access to a collection, reviewing
export requests, and managing policies on the collection.
As described above, stewards are pre-associated with a particular safe collection by
way of a specialized role and mapping to a collection's storage layer.
External users (e.g., analysts) can discover
and then obtain access to safe collections by listing available safe collections and requesting
access to individual collections.
Stewards for a safe collection are presented with a list of user requests and must explicitly approve access
for a specific duration. Throughout the duration of a user's access to a collection
stewards may review their actions and revoke access at any time. When users attempt
to export data from an export controlled safe-collection, the data is not immediately
accessible to the user. Rather, the exported data is collected and stored privately
assuming that it contains microdata, and is released pending review by a a steward.
